Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction

### 2019-11-25 docs/article.tex
últimos ajustes - pastas com imagens foram colocadas no caminho já

	\section{Introduction}	
		\par Breast Cancer is a kind of malignant tumor in which cells in the breast grow out of control. In a recent survey called GLOBOCAN \cite{GLOBOCAN} published in 2018 by the IARC, can be visualized the statistics about this type of cancer around the world. The study states that breast cancer is the second most incident type of cancer in the world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equaled to 626 679 (about 30\% of total). According to the same study, the breast cancer is the most incident type in Brazil, with 85 620 registered cases in total, and the second most reason of mortalities among the cancers, with 18 842 cases, what represents 22\% of the total cases of breast cancer in Brazil. Figures \ref{fig:graphic2} and \ref{fig:graphic1} in the right graph the information presented until now. In the first chart is possible to visualize the statistics about the world, and in the second one is presented the numbers of cases in Brazil.

@@

	\section{Feature Extraction}
        \par The Feature Extraction can be considered as one of the most important steps in Image Processing: this is the last phase before the classification of the samples. So, the main objective here is to compose feature vectors capable to describe the samples, to classify correctly each example in its real class.
        \par Commonly, two approaches can be chosen to extract descriptors from an image: Handcrafted Features and Non-Handcrafted ones. The Handcrafted Features, as the name claims, are the descriptors extracted manually, according to the choice of the developer, while the Non-Handcrafted Features are extracted automatically, to do the best possible classification (one example of this approach are the Convolutional Neural Networks - CNN).
		\par As mentioned in the title of this paper, the used approach for extracting the descriptors from the histopathological images was the handcrafted one, where 11 descriptors were extracted and used as the input of the classifiers. It is important to remember that the extraction was accomplished from segmented images and non-segmented ones, so, it is possible to compare the impact of the segmentation step during the classification. Below are the extracted features used in the process.
		\par The descriptors used in the present process can be divided into 3 categories: First Order Measures, Second Order Measures and Others. The First Order Measures are the descriptors that consider just the gray level information about the pixels, not considering the spatial relationships among them. The Second Order Measures, instead of the first ones, consider the spatial relationships among the pixels, beyond the gray level property. These descriptors are extracted from the called Gray Level Co-occurrence Matrix (GLCM), that is responsible to store the frequency that a pixel with gray level \textbf{i} and other with gray level \textbf{j} occur in the image, separated for a distance \textbf{d}, in the direction\textbf{ $\theta$} \cite{conci2008computacao}. This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).
		\par The group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method. Three descriptors can be found in this last group: Fourier Descriptors, Local Binary Pattern Features and Fractal Dimension Descriptors. 
		\par The Fourier Descriptors (FD), as the name says, are the features extracted from the Fourier Transform, which is responsible to transform the visualization of the signal from the spatial domain to the frequency domain, to become possible to see the frequencies that compose the image. Different approaches can be chosen to extract the FD`s, in the present work the proposed process was as follows:
		\begin{itemize}
            \item The image was transformed to the frequency domain with the Fast Fourier Transform (FFT).
			\item Without doing the shift of the transformed, N coefficients in the middle of the spectrum was taken, so just the high frequencies were caught from the FFT. Doing this process, it is possible to reconstruct the image just with these high frequencies coefficients, that represent the edges inside the signal. In Figure \ref{fig:imagem_reconstrucao} it is possible to see the original image and the reconstructed one made from the descriptors.
			\item Lastly, the complex magnitude was computed for the coefficients.
		\end{itemize}

@@

	\section{Feature Selection}
        \par The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea. Providing the feature vectors with all attributes as input to the classifiers gives a high probability of the classification does not achieve good results. This can be explained from the so-called "Curse of Dimensionality": After a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.
		\par In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes. The next section presents the analysis made by the Relief, taking into consideration the performance of the classifiers.

>>>>

	\section{Introduction}	
		\par Breast Cancer is a kind of malignant tumor in which cells in the breast grow out of control. In a recent survey called GLOBOCAN \cite{GLOBOCAN} published in 2018 by the IARC, can be visualized the statistics about this type of cancer around the world. The study states that breast cancer is the second most incident type of cancer in the world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equals to 626 679 (about 30\% of total). According to the same study, the breast cancer is the most incident type in Brazil, with 85 620 registered cases in total, and the second most reason of mortalities among the cancers, with 18 842 cases, what represents 22\% of the total cases of breast cancer in Brazil. Figures \ref{fig:graphic1} and \ref{fig:graphic2} in the right graph the information presented until now. In the first chart is possible to visualize the statistics about the world, and in the second one is presented the numbers of cases in Brazil.

@@

	\section{Feature Extraction}
        \par The Feature Extraction can be considered as one of the most important steps in Image Processing: this is the last phase before the classification of the samples. So, the main objective here is to compose feature vectors capable to describe the samples, to classify correctly each example in its real class.
        \par Commonly, two approaches can be chosen to extract descriptors from an image: Handcrafted Features and Non-Handcrafted ones. The Handcrafted Features, as the name claims, are the descriptors extracted manually, according to the choice of the developer, while the Non-Handcrafted Features are extracted automatically, to do the best possible classification (one example of this approach are the Convolutional Neural Networks - CNN).
		\par As mentioned in the title of this paper, the used approach for extracting the descriptors from the histopathological images was the handcrafted one, where 11 descriptors were extracted and used as the input of the classifiers. It is important to remember that the extraction was accomplished from segmented images and non-segmented ones, so, it is possible to compare the impact of the segmentation step during the classification. Below are the extracted features used in the process.
		\par The descriptors used in the present process can be divided into 3 categories: First Order Measures, Second Order Measures and Others. The First Order Measures are the descriptors that consider just the gray level information about the pixels, not considering the spatial relationships among them. The Second Order Measures, instead of the first ones, consider the spatial relationships among the pixels, beyond the gray level property. These descriptors are extracted from the called Gray Level Co-occurrence Matrix (GLCM), that is responsible to store the frequency that a pixel with gray level \textbf{i} and other with gray level \textbf{j} occur in the image, separated for a distance \textbf{d}, in the direction\textbf{ $\theta$} \cite{conci2008computacao}. This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).
		\par The "others group" mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method. Three descriptors can be found in this last group: Fourier Descriptors, Local Binary Pattern Features and Fractal Dimension Descriptors. 
		\par The Fourier Descriptors (FD), as the name says, are the features extracted from the Fourier Transform, which is responsible to transform the visualization of the signal from the spatial domain to the frequency domain, to become possible to see the frequencies that compose the image. Different approaches can be chosen to extract the FD`s, in the present work the proposed process was as follows:
		\begin{itemize}
            \item The image was transformed to the frequency domain with the Fast Fourier Transform (FFT).
			\item Without doing the shift of the transformed, N coefficients in the middle of the spectrum was taken, so just the high frequencies were caught from the FFT. Doing this process, it is possible to reconstruct the image just with these high frequencies coefficients, that represent the edges inside the signal. In Figure \ref{fig:imagem_reconstrucao} it is possible to see the original image and the reconstructed one made from the descriptors.
			\item Lastly, the complex magnitude was computed for the coefficients.
		\end{itemize}

@@

	\section{Feature Selection}
        \par The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea to make a classification with all these descriptors. Providing the feature vectors with all attributes as input to the classifiers gives a high probability of the classification does not achieve good results. This can be explained from the so-called "Curse of Dimensionality": After a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.
		\par In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes. The next section presents the analysis made by the Relief, taking into consideration the performance of the classifiers.
